The Effect of the COVID-19 Pandemic on Influenza Vaccination Rates in the United States

### 2022-11-11 Manuscript/manuscript.tex
add race and year figures
age graph
fixed reference position
add methods

\section*{Keywords}
\label{sec:Keywords}
Influenza Vaccine, Vaccine Hesitancy, COVID-19, Two Sample Z-Test

@@

\section{Methods}
\label{sec:Methods}

\section{Results}
\label{sec:Results}

>>>>

\section*{Keywords}
\label{sec:Keywords}
Influenza Vaccine, Statistics, Two Proportion Z-Test, Vaccine Hesitancy,

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width= 125mm ,scale=.5]{plot.png}
  \caption{Influenza Vaccination Proportions of Those $\ge 6$ Months Old From 2019-2022.}
  \label{fig:years}
\end{figure}

\begin{figure}[ht!]
  \centering
  \includegraphics[width= 125mm ,scale=.75]{race.png}
  \caption{Influenza Vaccination Proportions by Race in 2019-2022.}
  \label{fig:race}
\end{figure}

\begin{figure}[ht!]
  \centering
  \includegraphics[width= 125mm ,scale=.5]{age.png}
  \caption{Influenza Vaccination Proportions by Age in 2019-2022.}
  \label{fig:age}
\end{figure}

\clearpage
\section{Methods}
\label{sec:Methods}
In order to determine if there was evidence of a significant difference in influenza vaccination proportions, a two proportion z test was conducted using R software. The
hypotheses tested were that there was no significant difference in population proportions verus there was a significant difference. A total of 18 tests were conducted.
The first test used the proportions of those vaccinated, who were 6 months or older, from 2019-2020, 2020-2021, and 2021-2022. More specfically, the sample proportion
for 2019-2020, .518, was compared to that of 2020-2021, .521. This step was repeated, but for 2020-2021 compared to 2021-2022.
\section{Results}
\label{sec:Results}
